---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ace2fastq)
```
# Introduction

A simple function for '.ace' files converts ABI 'Sanger' capillary sequence assembly files. Each file only contains one sequence and corresponding quality values.

The function expects as a minimum a full path to the .ace file. By default a corresponding file with .fastq extension instead of .ace will be created. Also by default, the id line in the fastq file start after the obligatory @ with the name of the original .ace file without the extension followed by the internal original id from the .ace file.

A default example follows:

```{r}
library(ace2fastq)

filename <- system.file("sampledat/1.seq.ace", package = "ace2fastq")

out_file <- ace_to_fastq(filename)

lines <- readLines(out_file)

```

```{r echo=FALSE}
# shortened lines
n <- 40
substr(lines[1], 1, n)
substr(lines[2], 60, 60+n)
substr(lines[3], 1, 1)
substr(lines[4], 60, 60+n)

```
A example with the alternative id pattern follows:

```{r}
library(ace2fastq)

filename <- system.file("sampledat/1.seq.ace", package = "ace2fastq")

out_file <- ace_to_fastq(filename, name2id = FALSE)

lines <- readLines(out_file)
```

```{r echo=FALSE}
substr(lines[1], 1, n)
```

The target directory path can also be changed.
